Bayesian Hierarchical Models for Common Components across Multiple System Configurations

### 2017-09-04 paperDraft2.tex
reorganized and reworded

Despite its common uses the assumption of a constant failure rate over time is
rarely justifiable.  It has been well documented the issues that can arise when
this assumption is violated ~\cite{ref2}.  Thus we will also consider the same
hierarchical model structure while using the Weibull distribution.  Now we
assume that the failure times $y_{ijk}$ each follow a $Weibull(\lambda, \gamma)$
distribution with scale parameter $\lambda$ and shape parameter $\gamma$, with
probability density function for Test Phase 1,
\begin{equation}
f(y_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
y_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} y_{ijk}^{\gamma_{i}})
\end{equation}
The Weibull distribution is a more flexible model with both a rate parameter
$\lambda_{ij}$ and a shape parameter $\gamma_{j}$.  The exponential is a special
case of the Weibull, when $\gamma = 1$.

@@

\subsubsection{Model Diagnostics}
So far we have discussed a number of different models and the assumptions that
accompany them.  We will now discuss the process of choosing a final model.  The
decision of which model to use can have a drastic impact on reliability
assessment and future test planning.  We will use the JLTV dataset to
demonstrate the process.

@@

\begin{tabular}{|l|l|r|}
\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
\cline{1-3}
Distribution    & Structure & DIC \\
\hline
Exponential   & Single Rate                       & 23258               \\
              & Hierarchical Rate                 & 23022               \\
Weibull       & Single Rate                       & 18750               \\
              & Hierarchical Rate                 & \textbf{18556}      \\
              & Hierarchical Rate (One shape)     & 18677               \\
\hline
\end{tabular}

@@

\subsubsection{JLTV Reliability Results}
*** TODO ***
Now that we have selected a model for the data we can use the posterior
distributions  of the systems parameters to estimate reliability-related
quantities of interest.

Expected miles to failure.

Plot comparing exponential results vs. Weibull.

\subsection{Assurance Test Planning}
In this section, we use the resulting reliability model from the previous section
develop a plan for future testing.  Here the objective is to demonstrate that at
a desired level of confidence, the system will meet or exceed a specified
requirement. The methods to be employed will be similar to the assurance testing
as discussed by Hamada et al. ~\cite{ref4}. Bayesian assurance tests are used to
ensure that the reliability of an item meets or exceeds a specified requirement
with a desired probability. Although practitioners often use ``assure'' and
``demonstrate'' synonymously, Meeker and Escobar ~\cite{ME04} distinguish
between reliability demonstration and reliability assurance testing. A
\emph{reliability demonstration test} is essentially a classical hypothesis
test, which uses only the data from the test to assess whether the
reliability-related quantity of interest meets or exceeds the requirement. A
\emph{reliability assurance test}, however, uses supplementary data and
information in order to test as efficient as possible.

In both classical and Bayesian test planning we are interested in controlling
error rates while minimizing the resources required for testing.  In the DoD
acquisition process, the error rates will be referenced in terms of risk.
\emph{Consumer risk} which considers the event of purchasing a product that does
not meet reliability requirements.  \emph{Producer risk} which considers the
event of a product with acceptable reliability failing a given test and not
being considered for purchase.  Introducing the notation for this section, In
the JLTV case study, we will be determining how many miles on test $T$, are
required and how many system failures to allow $c$, before the product is
considered unacceptable.  We will define $W(t)$ as a random variable that
represents the total number of system failures after $t$ miles.  Suppose that
$\pi$ denotes some quantity of interest that is related to system reliability at
a given time. It is common to base both classical and Bayesian test plans on two
specified levels of $\pi$: $\pi_0$, an \emph{acceptable reliability level}
(ARL), and $\pi_1$, a \emph{rejectable reliability level} (RRL), where $\pi_1
\leq  \pi_0$. Although the precise definition of ARL and RRL differ between the
classical and Bayesian test criteria, we use them in an equivalent way.

>>>>

Despite its common uses the assumption of a constant failure rate over time is
rarely justifiable.  It has been well documented the issues that can arise when
this assumption is violated ~\cite{ref2}.  Thus we will also consider the same
hierarchical model structure while using the Weibull distribution.  Now we
assume that the failure times $y_{ijk}$ each follow a $Weibull(\lambda, \gamma)$
distribution with scale parameter $\lambda$ and shape parameter $\gamma$, with
probability density function for Test Phase 1,
\begin{equation}
f(y_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
y_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} y_{ijk}^{\gamma_{i}}).
\end{equation}
The Weibull distribution is a more flexible model with both a rate parameter
$\lambda_{ij}$ and a shape parameter $\gamma_{j}$.  The exponential is a special
case of the Weibull, when $\gamma = 1$.

@@

\subsubsection{JLTV Reliability}
So far we have discussed a number of different models and the assumptions that
accompany them.  Using McMC we can fit each of these models to the JLTV dataset.
Then we can use the posterior distributions of the systems parameters to
estimate reliability-related quantities of interest.

Plot with expected miles to failure for each of 3 models to show the Weibull and
exponential give very different results.

\subsubsection{Model Diagnostics}
needs new transition into this section

We will now discuss the process of choosing a final model.  The
decision of which model to use can have a drastic impact on reliability
assessment and future test planning.  We will use the JLTV dataset to
demonstrate the process.

@@

\begin{tabular}{|l|l|r|}
\multicolumn{3}{c}{\textbf{Goodness of Fit}} \\
\cline{1-3}
Distribution    & Structure & DIC \\
\hline
Exponential   & Hierarchical Rate                 & 23022               \\
Weibull       & Hierarchical Rate                 & \textbf{18556}      \\
              & Hierarchical Rate (One shape)     & 18677               \\
\hline
\end{tabular}

@@

\subsection{Assurance Test Planning}
In this section, we use the resulting reliability model from the previous
section develop a plan for future testing.  Here the objective is to demonstrate
that at a desired level of confidence, the system will meet or exceed a
specified requirement. The methods to be employed will be similar to the
assurance testing as discussed by Hamada et al. ~\cite{ref4}. Bayesian
\emph{reliability assurance tests} are used to ensure that the reliability of
an item meets or exceeds a specified requirement with a desired probability.
Meeker and Escobar ~\cite{ME04} established the difference between this and the
more traditional  \emph{reliability demonstration test}.  The difference being
that the assurance test plan incorporates supplementary data and information,
where the demonstration test only uses test data.

In both test planning methods we are interested in controlling error rates while
minimizing the resources required for testing.  In the DoD acquisition process,
the error rates will be referenced in terms of risk. \emph{Consumer risk} which
considers the event of purchasing a product that does not meet reliability
requirements.  \emph{Producer risk} which considers the event of a product with
acceptable reliability failing a given test and not being considered for
purchase.  Introducing the notation for this section, In the JLTV case study, we
will be determining how many miles on test $T$, are required and how many system
failures to allow $c$, before the product is considered unacceptable.  We will
define $W(t)$ as a random variable that represents the total number of system
failures after $t$ miles.  Suppose that $\pi$ denotes some quantity of interest
that is related to system reliability at a given time. It is common to base both
classical and Bayesian test plans on two specified levels of $\pi$: $\pi_0$, an
\emph{acceptable reliability level} (ARL), and $\pi_1$, a \emph{rejectable
reliability level} (RRL), where $\pi_1 \leq  \pi_0$. Although the precise
definition of ARL and RRL differ between the classical and Bayesian test
criteria, we use them in an equivalent way.
